---
title: "Daniel P Hall Riggins, MD's CV"
author: Daniel P. Hall Riggins, MD
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(here) # Constructs paths to your project's files.
library(glue) # Glue offers interpreted string literals that are small, fast, and dependency-free. 
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = glue("{here(\"data\")}/"),  
  pdf_mode = params$pdf_mode
) 

CV$entries_data <-
    CV$entries_data |> 
    dplyr::filter(as.logical(medically_relevant))
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r}
# if(params$pdf_mode){
#   cat("View this [CV online](https://danielriggins.com/cv)")
# } else {
#   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://raw.githubusercontent.com/andtheWings/andtheWings.github.io/master/cv/cv.pdf)")
# }
```

Made with the R packages [\{pagedown\}](https://github.com/rstudio/pagedown) and [\{datadrivencv\}](http://nickstrayer.me/datadrivencv/)

Source code available on [github](https://github.com/andtheWings/adapted-datadrivencv)

Last updated on `r Sys.Date()`


Main
================================================================================

Daniel P. Hall Riggins, MD {#title}
---------------------------------------

Training {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Other Employment {data-icon=briefcase #employment}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('employment')
```

Honors and Awards {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```

Selected Projects {data-icon=search}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('projects')
```

Journal Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('pubs')
```

Selected Presentations {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

<!--
### Indiana Ave Community Survey ([slides](https://docs.google.com/presentation/d/1FNQX2FLx0By-fFqEsdiiuGdxNx1620Px5jWqWwBzifc/edit?usp=sharing))

Senior Presentation for Pediatrics Residency at Indiana University School of Medicine

Indianapolis, IN

2021

- Riggins, D.P.



### Obesity in Urban Youth: Connection to Enuresis ([poster](http://danielriggins.com/cv/prop/PAS%20poster%20enuresis%204-18-2019%20final.pptx))

Pediatric Academic Societies Meeting

Baltimore, MD

2019

- Gross, M., Riggins, D.P., Sims, C., Foreman, O., Rieder, J.

-->

### The relationship between incarceration and retention in opioid maintenance treatment ([slides](http://danielriggins.com/cv/prop/correctional_health_conference_slides.pptx))

9th Academic and Health Policy Conference on Correctional Health

Baltimore, MD

2016

- Riggins, D.P., Fox, A.D.

<!--

### The relationship between incarceration and opioid addiction treatment ([slides](http://danielriggins.com/cv/prop/bupe_riggins_150818.pptx))

New York Academy of Medicine's Medical Student Forum

New York City, NY

2015

- Riggins, D.P., Fox, A.D.

-->

### pH Regulation Differs Under Low Oxygen Conditions in E. Coli ([poster](http://danielriggins.com/cv/prop/Riggins_ASM_Poster_3.pptx))

112th General Meeting of the American Society for Microbiology

San Francisco, CA

2012

- Riggins, D.P., Martinez, K, Slonczewski, J.L.


<!--
### The Effects of Anoxic Conditions on the Extreme-Acid Survival of Escherichia coli (slides)

Kenyon College Biology Honors Student Presentations

Gambier, OH

2012

- Riggins, Slonczewski, J.L.
-->


Selected Extracurriculars {data-icon=hands-helping}
--------------------------------------------------------------------------------

### Volunteer

[VOICES](http://voicescorp.org/)

Indianapolis, IN

2021 - 2020

- Chaperoned systems-involved youth on a college visit 
- Mentored youth Leadership Fellows on an advocacy project regarding housing/homelessness

<!--
### Wellness Chair

IUSM Pediatrics Resident Council

Indianapolis, IN

2020 - 2018

- Coordinated improvements to resident workrooms like couches, lamps, mini-fridge, etc		
- Coordinated wellness sessions during noon conference such as time with dogs on the front lawn and a curriculum on spiritual care in medicine
-->


### Board Member

Einstein Social Medicine Lecture Series

Bronx, NY

2016 - 2014

- Coordinated lectures delivered by invited speakers on the following topics: healthcare for refugees, ethics of lethal injection, correctional health, and social implications of antimicrobial resistance


<!--
### Clinical Volunteer

Einstein Community Health Outreach Clinic

Bronx, NY

2018 - 2014

- Completed 15 sessions at Einstein's student-run free clinic for uninsured/undocumented patients
- During clinical years (3-4), provided primary care encounters for patients, ran back-of-house operations like laboratory/consult follow-up, and coordinated clinical flow
- During pre-clinical years (1-2), performed chart review for information on quality measures as well as initial patient intake and triage	

### Board Member

Einstein NICU Cuddling Club

Bronx, NY

2018 - 2014

- Acted as board member for 2015-2016 academic year, coordinating training and scheduling for program volunteers
- Personally provided 16 hours of supportive human touch for neonates in the Montefiore neonatal intensive care unit

-->

### Board Member

Health Education Outreach Program

Bethesda, MD

2014 - 2012

- Personally taught over 10 health lessons at homeless shelters in the Maryland suburbs of Washington D.C.
- As board member, helped with recruiting, training, and development of [organization web site](https://heopdmv.wordpress.com/about/)	
- As head teacher, coordinated scheduling, [wrote/edited content](http://danielriggins.com/cv/img/menshealth.pdf), and assigned responsibilities for a group of 5 teachers


<!--
### Educator and Gardener

Bronx, Obesity, Diabetes, and You (BODY)

Bronx, NY

2015 - 2012

- Taught local elementary students how to plant seeds and transplant them into BODY-run community garden
- Maintained the garden over summer months. Harvested produce and shared it with local community members

### Patient Ambassador

Clinical Center at the National Institutes of Health

Bethesda, MD

2014 - 2012

- In the radiology department, I transported people to imaging and back	
- In the surgery department, I stocked operating rooms with supplies and transported patients to/from their procedures	
- See a [brief feature](https://www.cc.nih.gov/about/news/newsletter/2014/apr2014/newsletter.html#story1) about volunteers including myself in the Clinical Center’s newsletter

### Dog Handler

People and Animals Cardio Klub (PACK) of the Humane Rescue Alliance

Washington, DC

2014 - 2012

- Picked up dogs from area shelters every Saturday morning and drove them to a meeting spot in Rock Creek National Park for a three-mile run	
- Sustained exercise helped the dogs with general health as well as temperament during subsequent adoption events	
-->

Coding Courses {data-icon=laptop}
---------------------------------------------------------------------------------

### Coursera:

Python for Everybody Specialization:

N/A

N/A

- Programming for Everybody
- Python Data Structures
- Using Python to Access Web Data
- Using Databases with Python

### DataCamp:

R:

N/A

N/A
  
- Introduction to R
- Intermediate R
- Introduction to the Tidyverse
- Data Manipulation with dplyr
- Interactive Maps with leaflet in R

**Python:**

- Introduction to Python
- Intermediate Python
- Streamlined Data Ingestion with pandas

**SQL:**

  - Introduction to SQL

<!--
Personal Interests {data-icon=bicycle}
---------------------------------------------------------------------------------

### Bicycling

For my commute, recreationally, and as an avenue for advocacy

N/A

N/A

### Citizen Science

Like the iNaturalist project 

N/A

N/A

### Gardening

I have a rain garden that serves as pollinator habitat 

N/A

N/A

### Mapping

Especially with the free OpenStreetMap project

N/A

N/A

### Open Source

Especially projects in the R language

N/A

N/A
-->