---
title: "Daniel P Hall Riggins, MD's CV"
author: Daniel P. Hall Riggins, MD
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: FALSE
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(here) # Constructs paths to your project's files.
library(glue) # Glue offers interpreted string literals that are small, fast, and dependency-free. 
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = glue("{here(\"data\")}/"),  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r}
if(params$pdf_mode){
  cat("View this [CV online](https://danielriggins.com/cv)")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://raw.githubusercontent.com/andtheWings/andtheWings.github.io/master/cv/cv.pdf)")
}
```

Made with the R packages [\{pagedown\}](https://github.com/rstudio/pagedown) and [\{datadrivencv\}](http://nickstrayer.me/datadrivencv/)

Source code available on [github](https://github.com/andtheWings/adapted-datadrivencv)

Last updated on `r Sys.Date()`


Main
================================================================================

Daniel P. Hall Riggins, MD {#title}
---------------------------------------

Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Honors and Awards {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```

Project Work {data-icon=search}
--------------------------------------------------------------------------------

### Cook County Recovery Home Coordinated Capacity Project

Cook County Health

Chicago, IL

Present - 2021

- Mentor: [Juleigh Nowinski-Konchak](https://cookcountyhealth.org/physicians/juleigh-m-nowinski-konchak-md/)
- Description: Acting as program manager for an intervention using navigators and capacity management software to improve the experience for clients seeking placement at substance use recovery homes
- Output: None (pilot of project still in progress)

### Evaluation of the Oak Park Medical Respite Center

Cook County Health

Oak Park, IL

2022 - 2021

- Mentor: [Keiki Hinami](https://cookcountyhealth.org/physicians/keiki-hinami-md-2/)
- Description: Generating descriptive statistics and an analysis of healthcare utilization for patients at CCH's medical respite center serving people experiencing homelessness
- Output: White paper (manuscript in progress)

### Project CHILD

Cook County Health

Chicago, IL

Present - 2021

- Mentor: [Bill Trick](https://cookcountyhealth.org/physicians/william-trick-md/)
- Description: Developing models of the geographic distribution of Sudden Infant Death Syndrome-related deaths in Cook County, IL
- Output: Oral presentations to Cook County Health and Chicago Dept of Public Health

### Community Survey of the Indiana Avenue Cultural District

Indiana University School of Medicine

Indianapolis, IN

2021 - 2020

- Mentor: [Tracey Wilkinson](https://medicine.iu.edu/faculty/23603/wilkinson-tracey)
- Description: Developed a survey that investigated local residents' vision for the central historic neighborhood of the Black community in Indianapolis
- Output: [IRB Protocol](http://danielriggins.com/IRB_for_Indy_Housing_Interviews/) and the [survey itself](https://iu.co1.qualtrics.com/jfe/form/SV_0cV3fmUkfeitwdE)

### Road Injury Safety in Indianapolis

Indiana University School of Medicine

Indianapolis, IN

2020 - 2018

- Mentors: [Randy Grout](https://www.regenstrief.org/person/randall-grout/), [Sarah Wiehe](https://medicine.iu.edu/faculty/16722/wiehe-sarah)
- Description: Performed [geospatial visualization](http://danielriggins.com/plotting_crashes.html) and [hot-spot analysis](http://danielriggins.com/KDEplus_Notebook) regarding pedestrian crashes around the Indianapolis Metropolitan area
- Output: Open access reports as above

### Adolescent Enuresis

Albert Einstein College of Medicine

Bronx, NY

2018 - 2017

- Mentor: [Jessica Rieder, M.D., M.S.](https://www.einstein.yu.edu/faculty/1063/jessica-rieder/)
- Description: Coordinated recruiting and performed data analysis for a survey investigating the rate of enuresis in the Montefiore teen population and related factors
- Output: Research [poster](http://danielriggins.com/cv/prop/PAS%20poster%20enuresis%204-18-2019%20final.pptx)

### Incarceration and Buprenorphine Therapy

Albert Einstein College of Medicine

Bronx, NY

2016 - 2015

- Mentor: [Aaron D. Fox, M.D.](https://www.einstein.yu.edu/faculty/11501/aaron-fox/)
- Description: Directed a post-hoc analysis of a cohort of patients receiving integrated treatment for HIV and opioid use disorder; the study asked how recent incarceration affected outcomes for buprenorphine replacement therapy
- Outputs: [Two](http://danielriggins.com/cv/prop/bupe_riggins_150818.pptx) [presentations](http://danielriggins.com/cv/prop/correctional_health_conference_slides.pptx), first authorship on [journal publication](http://www.tandfonline.com/doi/full/10.1080/08897077.2016.1220443), and research award from my medical school

### *Staphylococcal* Genetics

Food and Drug Administration, Center for Biologics Evaluation and Research

Bethesda, MD

2014 - 2012

- Mentors: Roger D. Plaut, Ph.D. and [Scott Stibitz, Ph.D.](https://www.fda.gov/vaccines-blood-biologics/biologics-research-projects/bacterial-vaccine-safety-biomarkers-virulence-and-attenuation-bordetella-pertussis-whooping-cough)
- Description: As in [employment section](danielriggins.com/cv#employment)
- Outputs: Authorship on [two](http://www.cell.com/cell-host-microbe/fulltext/S1931-3128(17)30441-9) [papers](https://mbio.asm.org/content/10/1/e02491-18)

### Acid Survival of *E. coli*

Kenyon College

Gambier, OH

2013 - 2008

- Mentor: [Joan L. Slonczewski, Ph.D.](https://www.kenyon.edu/directories/campus-directory/biography/joan-slonczewski/)
- Description: Led a project investigating how anaerobic conditions affect the acid survival response in E. coli
- Outputs: [Honors thesis](https://digital.kenyon.edu/honorstheses/76/), [poster presentation](http://danielriggins.com/cv/prop/Riggins_ASM_Poster_3.pptx), [two](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0010132) [papers](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0056796) with first authorship on the second one, and research award from my undergraduate college

Journal Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('pubs')
```

Presentations {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Indiana Ave Community Survey ([slides](https://docs.google.com/presentation/d/1FNQX2FLx0By-fFqEsdiiuGdxNx1620Px5jWqWwBzifc/edit?usp=sharing))

Senior Presentation for Pediatrics Residency at Indiana University School of Medicine

Indianapolis, IN

2021

- Riggins, D.P.

### Obesity in Urban Youth: Connection to Enuresis ([poster](http://danielriggins.com/cv/prop/PAS%20poster%20enuresis%204-18-2019%20final.pptx))

Pediatric Academic Societies Meeting

Baltimore, MD

2019

- Gross, M., Riggins, D.P., Sims, C., Foreman, O., Rieder, J.

### The relationship between incarceration and retention in opioid maintenance treatment ([slides](http://danielriggins.com/cv/prop/correctional_health_conference_slides.pptx))

9th Academic and Health Policy Conference on Correctional Health

Baltimore, MD

2016

- Riggins, D.P., Fox, A.D.

### The relationship between incarceration and opioid addiction treatment ([slides](http://danielriggins.com/cv/prop/bupe_riggins_150818.pptx))

New York Academy of Medicine's Medical Student Forum

New York City, NY

2015

- Riggins, D.P., Fox, A.D.

### pH Regulation Differs Under Low Oxygen Conditions in E. Coli ([poster](http://danielriggins.com/cv/prop/Riggins_ASM_Poster_3.pptx))

112th General Meeting of the American Society for Microbiology

San Francisco, CA

2012

- Riggins, D.P., Martinez, K, Slonczewski, J.L.

### The Effects of Anoxic Conditions on the Extreme-Acid Survival of Escherichia coli (slides)

Kenyon College Biology Honors Student Presentations

Gambier, OH

2012

- Riggins, Slonczewski, J.L.


Employment {data-icon=briefcase #employment}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('employment')
```

Extracurriculars {data-icon=hands-helping}
--------------------------------------------------------------------------------

### Volunteer

[VOICES](http://voicescorp.org/)

Indianapolis, IN

2021 - 2020

- Mentored Youth Leadership Fellows on an advocacy Project regarding housing/homelessness

### Wellness Chair

IUSM Pediatrics Resident Council

Indianapolis, IN

2020 - 2018

- Coordinated improvements to resident workrooms like couches, lamps, mini-fridge, etc		
- Coordinated wellness sessions during noon conference such as time with dogs on the front lawn and a curriculum on spiritual care in medicine

### Board Member

Einstein Social Medicine Lecture Series

Bronx, NY

2016 - 2014

- Coordinated lectures delivered by invited speakers on the following topics: healthcare for refugees, ethics of lethal injection, correctional health, and social implications of antimicrobial resistance

### Clinical Volunteer

Einstein Community Health Outreach Clinic

Bronx, NY

2018 - 2014

- Completed 15 sessions at Einstein's student-run free clinic for uninsured/undocumented patients
- During clinical years (3-4), provided primary care encounters for patients, ran back-of-house operations like laboratory/consult follow-up, and coordinated clinical flow
- During pre-clinical years (1-2), performed chart review for information on quality measures as well as initial patient intake and triage	

### Board Member

Einstein NICU Cuddling Club

Bronx, NY

2018 - 2014

- Acted as board member for 2015-2016 academic year, coordinating training and scheduling for program volunteers
- Personally provided 16 hours of supportive human touch for neonates in the Montefiore neonatal intensive care unit

### Board Member

Health Education Outreach Program

Bethesda, MD

2014 - 2012

- Personally taught over 10 health lessons at homeless shelters in the Maryland suburbs of Washington D.C.
- As board member, helped with recruiting, training, and development of [organization web site](https://heopdmv.wordpress.com/about/)	
- As head teacher, coordinated scheduling, [wrote/edited content](http://danielriggins.com/cv/img/menshealth.pdf), and assigned responsibilities for a group of 5 teachers

### Educator and Gardener

Bronx, Obesity, Diabetes, and You (BODY)

Bronx, NY

2015 - 2012

- Taught local elementary students how to plant seeds and transplant them into BODY-run community garden
- Maintained the garden over summer months. Harvested produce and shared it with local community members

### Patient Ambassador

Clinical Center at the National Institutes of Health

Bethesda, MD

2014 - 2012

- In the radiology department, I transported people to imaging and back	
- In the surgery department, I stocked operating rooms with supplies and transported patients to/from their procedures	
- See a [brief feature](https://www.cc.nih.gov/about/news/newsletter/2014/apr2014/newsletter.html#story1) about volunteers including myself in the Clinical Center’s newsletter

### Dog Handler

People and Animals Cardio Klub (PACK) of the Humane Rescue Alliance

Washington, DC

2014 - 2012

- Picked up dogs from area shelters every Saturday morning and drove them to a meeting spot in Rock Creek National Park for a three-mile run	
- Sustained exercise helped the dogs with general health as well as temperament during subsequent adoption events	

Coding Courses {data-icon=laptop}
---------------------------------------------------------------------------------

### Coursera:

Python for Everybody Specialization:

N/A

N/A

- Programming for Everybody
- Python Data Structures
- Using Python to Access Web Data
- Using Databases with Python

### DataCamp:

R:

N/A

N/A
  
- Introduction to R
- Intermediate R
- Introduction to the Tidyverse
- Data Manipulation with dplyr
- Interactive Maps with leaflet in R

**Python:**

- Introduction to Python
- Intermediate Python
- Streamlined Data Ingestion with pandas

**SQL:**

  - Introduction to SQL

Personal Interests {data-icon=bicycle}
---------------------------------------------------------------------------------

### Bicycling

For my commute, recreationally, and as an avenue for advocacy

N/A

N/A

### Citizen Science

Like the iNaturalist project 

N/A

N/A

### Gardening

I have a rain garden that serves as pollinator habitat 

N/A

N/A

### Mapping

Especially with the free OpenStreetMap project

N/A

N/A

### Open Source

Especially projects in the R language

N/A

N/A


