---
title: "Daniel P Hall Riggins, MD, MPH"
author: Daniel P. Hall Riggins, MD, MPH
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ['resume', 'dd_cv.css']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(here) # Constructs paths to your project's files.
library(glue) # Glue offers interpreted string literals that are small, fast, and dependency-free. 
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = glue("{here(\"data\")}/"),  
  pdf_mode = params$pdf_mode
) 

CV$entries_data <-
    CV$entries_data |> 
    dplyr::filter(as.logical(medically_relevant))
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

```{r}
# if(params$pdf_mode){
#   cat("View this [CV online](https://danielriggins.com/cv)")
# } else {
#   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://raw.githubusercontent.com/andtheWings/andtheWings.github.io/master/cv/cv.pdf)")
# }
```

Made with the R packages [\{pagedown\}](https://github.com/rstudio/pagedown) and [\{datadrivencv\}](http://nickstrayer.me/datadrivencv/)

Source code available on [github](https://github.com/andtheWings/adapted-datadrivencv)

Last updated on `r Sys.Date()`


Main
================================================================================

Daniel P. Hall Riggins, MD, MPH {#title}
---------------------------------------

<p id="boardCert">Board certified in pediatrics and board-eligible in preventive medicine</p>

Employment {data-icon=briefcase #employment}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('employment')
```

<!-- Designed, cloned, and expressed several markerless insertion/deletion mutations in Staphylococcus -->
<!-- Generated large pool of Staphylococcus mutants via transposon mutagenesis -->
<!-- FDA Address: 10903 New Hampshire Ave, Silver Spring, MD 20993 -->
<!-- Scott Stibitz, Principal Investigator of Laboratory of Mucosal Pathogens & Cellular Immunology, 240-402-7401, Earle.Stibitz@fda.hhs.gov -->
<!-- Term: July 11th, 2012 - June 27th, 2014 -->

Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

<!-- Prev Med Address: 1950 W. Polk St, Chicago, IL 60612 -->

<!-- Prev Med Duties: -->
<!-- - Project Work: 60% FTE on public health projects as outlined in my CV -->
<!-- - Educational: 20% FTE on classwork for a master of public health degree -->
<!-- - Clinical: 20% FTE on clinical work in pediatric primary care, preventive services for migrant children, and care coordination for people experiencing homelessness -->

<!-- Pediatric Residency Address: 1130 W Michigan Street, Fesler Hall 320, Indianapolis, IN 46202 -->
<!-- Jerry Rushton, jrushton@iu.edu, 317-944-4034 -->
<!-- Pediatric Residency Duties: Clinical practice to cover the breadth of general pediatrics training including primary care, emergency department, general hospital ward, specialty care services, and intensive care units. -->

Honors and Awards {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```

Journal Publications {data-icon=book-open}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('pubs')
```

Manuscripts {data-icon=scroll}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('manuscripts')
```


Selected Projects {data-icon=search}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('projects')
```

Selected Presentations {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('presentations')
```


Selected Extracurriculars {data-icon=hands-helping}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('extracurriculars')
```

<!--

### Volunteer

[VOICES](http://voicescorp.org/)

Indianapolis, IN

2021 - 2020

- Chaperoned systems-involved youth on a college visit 
- Mentored youth leadership fellows on an advocacy project regarding housing/homelessness


### Wellness Chair

IUSM Pediatrics Resident Council

Indianapolis, IN

2020 - 2018

- Coordinated improvements to resident workrooms like couches, lamps, mini-fridge, etc		
- Coordinated wellness sessions during noon conference such as time with dogs on the front lawn and a curriculum on spiritual care in medicine



### Board Member

Einstein Social Medicine Lecture Series

Bronx, NY

2016 - 2014

- Coordinated lectures delivered by invited speakers on the following topics: healthcare for refugees, ethics of lethal injection, correctional health, and social implications of antimicrobial resistance


### Clinical Volunteer

Einstein Community Health Outreach Clinic

Bronx, NY

2018 - 2014

- Completed 15 clinical sessions at Einstein's student-run free clinic for uninsured/undocumented patients
- During clinical years (3-4), provided primary care encounters for patients, ran back-of-house operations like laboratory/consult follow-up, and coordinated clinical flow
- During pre-clinical years (1-2), performed chart review for information on quality measures as well as initial patient intake and triage

### Board Member

Einstein NICU Cuddling Club

Bronx, NY

2018 - 2014

- Acted as board member for 2015-2016 academic year, coordinating training and scheduling for program volunteers
- Personally provided 16 hours of supportive human touch for neonates in the Montefiore neonatal intensive care unit


### Board Member

Health Education Outreach Program

Bethesda, MD

2014 - 2012

- Personally taught 10 health lessons at homeless shelters in the Maryland suburbs of Washington D.C.
- As board member, helped with recruiting, training, and development of [organization web site](https://heopdmv.wordpress.com/about/)	
- As head teacher, coordinated scheduling, [wrote/edited content](http://danielriggins.com/cv/img/menshealth.pdf), and assigned responsibilities for a group of 5 teachers



### Educator and Gardener

Bronx, Obesity, Diabetes, and You (BODY)

Bronx, NY

2015 - 2012

- Taught local elementary students how to plant seeds and transplant them into BODY-run community garden
- Maintained the garden over summer months. Harvested produce and shared it with local community members

### Patient Ambassador

Clinical Center at the National Institutes of Health

Bethesda, MD

2014 - 2012

- In the radiology department, I transported people to imaging and back	
- In the surgery department, I stocked operating rooms with supplies and transported patients to/from their procedures	
- See a [brief feature](https://www.cc.nih.gov/about/news/newsletter/2014/apr2014/newsletter.html#story1) about volunteers including myself in the Clinical Center’s newsletter

### Dog Handler

People and Animals Cardio Klub (PACK) of the Humane Rescue Alliance

Washington, DC

2014 - 2012

- Picked up dogs from area shelters every Saturday morning and drove them to a meeting spot in Rock Creek National Park for a three-mile run	
- Sustained exercise helped the dogs with general health as well as temperament during subsequent adoption events	
-->

<!-- Coding Courses {data-icon=laptop} -->
<!-- --------------------------------------------------------------------------------- -->

<!-- ### Coursera: -->

<!-- Python for Everybody Specialization: -->

<!-- N/A -->

<!-- N/A -->

<!-- - Programming for Everybody -->
<!-- - Python Data Structures -->
<!-- - Using Python to Access Web Data -->
<!-- - Using Databases with Python -->

<!-- ### DataCamp: -->

<!-- R: -->

<!-- N/A -->

<!-- N/A -->

<!-- - Introduction to R -->
<!-- - Intermediate R -->
<!-- - Introduction to the Tidyverse -->
<!-- - Data Manipulation with dplyr -->
<!-- - Interactive Maps with leaflet in R -->

<!-- **Python:** -->

<!-- - Introduction to Python -->
<!-- - Intermediate Python -->
<!-- - Streamlined Data Ingestion with pandas -->

<!-- **SQL:** -->

<!--   - Introduction to SQL -->


Personal Interests {data-icon=bicycle}
---------------------------------------------------------------------------------

### Bicycling

For my commute, recreationally, and as an avenue for advocacy

N/A

N/A

### Citizen Science

Like the iNaturalist project 

N/A

N/A

### Gardening

I have a rain garden that serves as pollinator habitat 

N/A

N/A

### Mapping

Especially with the free OpenStreetMap project

N/A

N/A

### Open Source

Especially projects in the R language

N/A

N/A
